Statistical Analysis Script

### 2024-03-25 code/analysis-code/statistical-analysis.qmd
Module 11 Discussion
I made some updates based on the summary we have to write about our project.

---
title: "Statistical Analysis Script"
author: "Taylor Glass and Arlyn Santiago"
date: "03/12/24"
output: html_document
---
## Load necessary packages
```{r}
#| message: false
library(broom) #for cleaning up output from lm()
library(here) #for data loading/saving
library(tidymodels) # for model building 
```

@@

# create a data frame with the predictions and true values of Y
popdata <- bind_cols(poppred, mydata$sarc_standard) %>%
            rename(sarc_standard = "...2")

# find RMSE and R squared to determine model fit
rmse1 <- rmse(popdata, truth = sarc_standard, estimate = .pred)

# create predictions using the pct_currentlymarriedd predictor model
marriedpred <- predict(lmfit3, new_data = mydata) %>% 
                  select(.pred)

# create a data frame with the predictions and true values of Y
marrieddata <- bind_cols(marriedpred, mydata$pct_currentlymarried) %>%
            rename(pct_currentlymarried = "...2")

# find RMSE and R squared to determine model fit
rmse2 <- rmse(marrieddata, truth = pct_currentlymarried, estimate = .pred)

# compare the metrics 
print(rmse1)
print(rmse2)
```

>>>>

---
title: "Statistical Analysis Script"
author: "Taylor Glass and Arlyn Santiago"
date: "03/12/24"
output: html_document
---
## Load necessary packages
```{r}
#| message: false
library(dplyr) # for basic syntax
library(broom) #for cleaning up output from lm()
library(here) #for data loading/saving
library(tidymodels) # for model building 
```

@@

# create a data frame with the predictions and true values 
popdata <- bind_cols(poppred, mydata$sarc_standard) %>%
            rename(sarc_standard = "...2")

# find RMSE and R squared to determine model fit
rmse1 <- rmse(popdata, truth = sarc_standard, estimate = .pred)
rsq1 <- rsq(popdata, truth = sarc_standard, estimate = .pred)

# create predictions using the pct_currentlymarried predictor model
marriedpred <- predict(lmfit3, new_data = mydata) %>% 
                  select(.pred)

# create a data frame with the predictions and true values 
marrieddata <- bind_cols(marriedpred, mydata$pct_currentlymarried) %>%
            rename(pct_currentlymarried = "...2")

# find RMSE and R squared to determine model fit
rmse2 <- rmse(marrieddata, truth = pct_currentlymarried, estimate = .pred)
rsq2 <- rsq(marrieddata, truth = pct_currentlymarried, estimate = .pred)

# create predictions using the rate of maternal deaths predictor model
matdeathspred <- predict(lmfit5, new_data = mydata) %>% 
                  select(.pred)

# create a data frame with the predictions and true values 
matdeathdata <- bind_cols(matdeathspred, mydata$rate_matdeaths) %>%
            rename(rate_matdeaths = "...2")

# find RMSE and R squared to determine model fit
rmse3 <- rmse(matdeathdata, truth = rate_matdeaths, estimate = .pred)
rsq3 <- rsq(matdeathdata, truth = rate_matdeaths, estimate = .pred)

# compare the metrics 
print(rmse1)
print(rsq1)
print(rmse2)
print(rsq2)
print(rmse3)
print(rsq3)
```
